---
title: "Vinyl Record Popularity Over Time"
output: html_notebook
---
#Firstly, I started with activating packages that I will use.
```{r}
library(gtrendsR)
library(ggplot2)
```

#Next, I imported and cleaned my data. My first analysis was for vinyl record search popularity worldwide from 2014-2022.
```{r}
google.trends = gtrends(c("vinyl.record"), gprop = "web", time = "all")[[1]]
google.trends = dcast(google.trends, date ~ keyword + geo, value.var = "hits")
```

#Next, I explored the data.
```{r}
head(google.trends) #top rows
summary(google.trends) #column summaries
str(google.trends) #structure of the dataset
```
#Next, I plotted the data.
```{r}
ggplot(google.trends, aes(x=date)) + geom_line(aes(y= vinyl.record_world))+
  xlab("Year")+
  ylab("Num of searches")+
  ggtitle("Vinyl Record Popularity Over Time- Worldwide")
```

#Vinyl record searches have greatly reduced over the years with them peaking in late 2004. Next, I was interested in vinyl record searches categorized by country. I chose 2 of the biggest music markets in the world: USA and UK; to also get a comparison for popularity in different continents. Then, I imported and cleaned the new data.
```{r}
google.trends.country = gtrends(c("vinyl.record"), geo = c("US", "GB"), gprop = "web", time = "all")[[1]]
google.trends.country = dcast(google.trends.country, date ~ keyword+ geo, value.var = "hits")
```

#Next, I explored the data.
```{r}
head(google.trends.country) #top rows
summary(google.trends.country) #column summaries
str(google.trends.country) #structure of the dataset
```
#Next, I plotted the data.
```{r}
ggplot(google.trends.country,aes(x=date)) +       geom_line(aes(y= vinyl.record_US), colour="Blue")+
  geom_line(aes(y=vinyl.record_GB), colour="Red")+
  xlab("Year")+
  ylab("Num of searches")+
  ggtitle("Vinyl Record Popularity Over Time- US vs. UK")
```

#Vinyl record searches are more prevalant in the UK over the last few years compared to the US. Great R beginner project!
